---
title: GABAergic disinhibition from the BNST to PNOCARC neurons promotes HFD-induced hyperphagia
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: "hide"
    fig_width: 10
    fig_height: 7
params:
  dev: FALSE
---

```{r setup, include = FALSE}
library(targets)
library(magrittr)
source("functions.R")
# Do not print any console output
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
print_all <- !params$dev
rmyknife::make()
rmyknife::set_ggplot_defaults()
```

Calcium imaging data analysis and figures for the paper "GABAergic disinhibition from the BNST to PNOCARC neurons promotes HFD-induced hyperphagia".

## Calcium Imaging Analysis {.tabset}

### Changelog

2024-04-04
  - Created public repo for calcium imaging data analysis and figures

### Figure 3

#### Figure 3D

```{r fig3d, eval=print_all}
tar_read(lineplot_pattern_neurons_intervention)
```

#### Figure 3E

```{r fig3e, eval=print_all}
tar_read(plot_neurons_intervention_pattern_percentage)
```

#### Figure 3F

```{r fig3f, eval=print_all}
tar_read(plot_heatmap_neuron_intervention_paper)
```

#### Figure 3G

```{r fig3g, eval=print_all}
tar_read(plot_zscores_intervention_per_pattern_refeeding)
```

### Figure 4

#### Figure 4B

```{r fig4b, eval=print_all}
tar_read(lineplot_pattern_neurons_gastric_infusion_ensure)
```

#### Figure 4C

```{r fig4c, eval=print_all}
tar_read(plot_neurons_gastric_infusion_narrowed_pattern_percentage)
```

#### Figure 4D

```{r fig4d, eval=print_all}
tar_read(plot_zscore_gastric_infusion_narrowed_ggbetweenstats)
```

#### Figure 4E

```{r fig4e, eval=print_all}
tar_read(plot_neurons_gastric_infusion_narrowed_delta_baseline_vs_postgi)
```

#### Figure 4F

```{r fig4f, eval=print_all}
tar_read(plot_tiled_heatmap_gastric_infusion_ensure)
```

#### Figure 4G

```{r fig4g, eval=print_all}
tar_read(plot_zscores_gastric_infusion_narrowed_per_pattern_ensure_combined)
```

### SEM's

```{r sems, eval=print_all}
tar_read(sems_paper) %>%
  knitr::kable()
```


### Targets Dependency Graph

```{r visnetwork}
# Print only when new targets were made or we have production output
if (print_all) {
  tar_visnetwork()
}
```